An Online Visual Loop Closure Detection Method for Indoor Robotic Navigation

### 2014-12-02 latex-spie/article.tex
almost finished

\begin{abstract}
In this paper, we present an enhanced loop closure method\footnote{Readers can access the source code from the following link: \\https://github.com/ituroboticslab/Quantized-Local-Zernike-Moments} based on image-to-image matching  relies on Quantized Local Zernike Moments. In contradistinction to the previous methods, our approach uses additional depth information to extract Zernike Moments in local manner. These moments are used to represent holistic shape information inside the image. The complex moments that are extracted from both gray and depth images are coarsely quantized. In order to find out the similarity between two locations, Nearest Neighbour classification algorithm is performed. Examplary results and the practical implementation case of the method are also given with the data gathered on the testbed using a Kinect. The method is evaluated in three different datasets of different lighting conditions. Additional depth information beside the actual image increases the detection rate especially in dark. The results are referred as a successful, high-fidelity online method for visual place recognition as well as to close navigation loops, which is a crucial information for the well known Simultaneously Localization and mapping (SLAM) problem. This technique is quite simple because of its low computational complexity, and performs in real-time with high loop closing accuracy.

@@

The method implemented in this paper has been evaluated on three datasets which lighting conditions are different from each other. The tests are done with either using grayscale and depth images separately or using both of them. After that, the difference matrices are calculated to examine the results. Nearest Neighbour (NN) algorithm is applied to classify the new locations using the $L_{1}$ distance metric. In addition to this, the last 100 frames are not included in the classification phase, because it the sensor is always moving and these frames correspond to the area behind the sensor.

@@

The results are obtained by three datasets in which the trajectory of the Kinect mounted moving platform is similar to each Dataset that is created in different lightning conditions: Bright, Dim and Dark. In the first loop, there are no loop closures to detect. To examine the performance of the method, precision-recall (PR) curves are plotted for each dataset. The PR curves are illustrated in Figures \ref{subfig:pr_bright}, \ref{subfig:pr_dim}, \ref{subfig:pr_dark} in which there are compared three different image sources that are only grayscale images, only depth images and both. The results show that using both grayscale and depth images gives the best performance in bright and dim datasets. In addition to this, the similarity matrices calculated from each dataset is shown in \ref{fig:dist_matrices}. The black dots corresponds to the detected loop closures at $90\%$ precision. As it can be seen in the similarity matrices, the algorithm performs quite successful results to detect loop closure event.

@@

There exist limited number of techniques that operate in real-time without parallelization. The speed tests are done with a MacBook Pro 7.1 which specifications are Intel Core 2 Duo 2.4 GHz CPU. In this setting, the extraction of Quantized local Zernike moments of an image of size $256\times 192$ pixels takes approximately $10ms$. The NN classification is applied with simple brute-force searching in which the algorithmic complexity is $\mathcal{O}(mn)$ that depends on the number of frames to compare with. In other words, the amount of time needed to performs this search increases throughout the trajectory. Therefore, the total processing time including the brute force search is $14ms$ in average when approximately 2000 frames are processed.

@@

        \hspace{-2mm}
        \caption{Similarity matrices of the captured images in experimental results. Condensed gray shades point out to positive alikeness between scenes. The black dots in lower triangle indicates detected loop closures at $90\%$ precision.}
        \label{fig:dist_matrices}
\end{figure}

@@

In conclusion, this paper presents a novel image description technique that is used to achieve loop closure detection within a SLAM framework. The technique works quite rapidly and operates in real-time. Moreover, it results successful loop closing on different lightning conditions by using the depth information.

@@

Authors would like to thank for the collaboration and the equipments to ITU Robotics Laboratory, and Borda Technology for the indoor dataset retrieval.

>>>>

\begin{abstract}
In this paper, we present an enhanced loop closure method\footnote{Readers can access the source code from the following link: \\https://github.com/ituroboticslab/Quantized-Local-Zernike-Moments} based on image-to-image matching  relies on quantized local Zernike moments. In contradistinction to the previous methods, our approach uses additional depth information to extract Zernike moments in local manner. These moments are used to represent holistic shape information inside the image. The moments in complex space that are extracted from both grayscale and depth images are coarsely quantized. In order to find out the similarity between two locations, nearest neighbour (NN) classification algorithm is performed. Exemplary results and the practical implementation case of the method are also given with the data gathered on the testbed using a Kinect. The method is evaluated in three different datasets of different lighting conditions. Additional depth information with the actual image increases the detection rate especially in dark environments. The results are referred as a successful, high-fidelity online method for visual place recognition as well as to close navigation loops, which is a crucial information for the well known simultaneously localization and mapping (SLAM) problem. This technique is also practically applicable because of its low computational complexity, and performing capability in real-time with high loop closing accuracy.

@@

The method implemented in this paper has been evaluated on three datasets which lighting conditions are different from each other. The tests are done with either using gray and depth images separately or using both of them. After that, the difference matrices are calculated to examine the results. The NN algorithm is applied to classify the new locations using the $L_{1}$ distance metric. In addition to this, the last 100 frames are not included in the classification phase, because it the sensor is always moving and these frames correspond to the area behind the sensor.

@@

The results are obtained by three datasets for which the trajectory is similar. Each dataset that is created in different lightning conditions: Bright, Dim and Dark. In the first loop, there are no loop closures to detect. To examine the performance of the method, precision-recall (PR) curves are plotted for each dataset. The PR curves are illustrated in Figures \ref{subfig:pr_bright}, \ref{subfig:pr_dim}, \ref{subfig:pr_dark} in which there are compared three different image sources that are only grayscale images, only depth images and both. The results show that using both grayscale and depth images gives the best performance in bright and dim datasets. In addition to this, the similarity matrices calculated from each dataset is shown in Figure \ref{fig:dist_matrices}. The black dots corresponds to the detected loop closures at $90\%$ precision. As it can be seen in the similarity matrices, the algorithm performs quite successful results to detect loop closure event.

@@

There exist limited number of techniques that operate in real-time without parallelization. The speed tests are done with a MacBook Pro 7.1 Intel Core 2 Duo 2.4 GHz CPU. In this setting, the extraction of quantized local Zernike moments of an image of size $256\times 192$ pixels takes approximately $10ms$. The NN classification is applied with simple brute-force searching in which the algorithmic complexity is $\mathcal{O}(n)$ that depends on the number of frames to compare with. In other words, the amount of time needed to performs this search increases throughout the trajectory. Therefore, the total processing time including the brute force search is $14ms$ in average when approximately 2000 frames are processed.

@@

        \hspace{-2mm}
        \caption{Similarity matrices of the captured images in experimental results. Condensed gray shades denotes the positive alikeness between scenes. The black dots in lower triangle indicates detected loop closures at $90\%$ precision.}
        \label{fig:dist_matrices}
\end{figure}

@@

In conclusion, this paper presents a novel image description technique that is used to achieve loop closure detection within a SLAM framework. The technique performs rapidly and operates in real-time. Moreover, loop closure is done successfully on all the lighting conditions with the help of the depth information used.

@@

Authors would like to thank for the collaboration and the equipments to ITU Robotics Laboratory, and Borda Technology for the help with indoor dataset retrieval.
